Erratum: A High-Order Discontinuous Galerkin Solver with Dynamic Adaptive Mesh Refinement to Simulate Cloud Formation Processes

### 2023-11-24 writing/erratum/CP032.tex
Some minor edits to erratum

\documentclass[runningheads]{llncs}
\title{Erratum: A High-Order Discontinuous Galerkin Solver with Dynamic Adaptive Mesh Refinement to Simulate Cloud Formation Processes }
\titlerunning{A High-Order DG Solver to Simulate Cloud Formation Processes}
\author{Lukas Krenz\orcidID{0000-0001-6378-0778} \and Leonhard Rannabauer \and Michael Bader}
\authorrunning{L.\ Krenz, L.\ Rannabauer, M.\ Bader}
\institute{Department of Informatics, Technical University of Munich\\
  \email{lukas.krenz@in.tum.de}, \email{rannabau@in.tum.de}, \email{bader@in.tum.de}
} 
\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage[american]{babel}
\usepackage[autostyle, english = american]{csquotes}
% \usepackage[%
%   backend=biber,
%   url=false,
%   doi=false,
%   % style=alphabetic,
%   % backref=true,
%   % hyperref=true,
%   maxnames=3,
%   % minnames=3,
%   % maxbibnames=99,
%   firstinits=true,
%   % uniquename=init
%   ]{biblatex}
% \addbibresource{../bibliography.bib}
\usepackage{cite}
\usepackage{todonotes}

@@

\begin{figure}[htb]
  \begin{subfigure}[t]{0.45\columnwidth}
  \includegraphics[width=\textwidth]{screenshots/cosine_bubble_2d_dg.png}
  \caption{\label{fig:cosine-bubble-2d-dg-amr}%
  2D Cosine bubble with AMR, computed by the ADER-DG method.
  Contours are at $-0.05, 0.05, \ldots 0.45$.
  }
  \end{subfigure}\quad
  \begin{subfigure}[t]{0.45\columnwidth}
  \includegraphics[width=1\textwidth]{screenshots/cosine_bubble_3d_dg.png}
  \caption{\label{fig:cosine-bubble-3d-dg-noamr}%
  3D Cosine bubble without AMR, computed by the ADER-DG method.}
  \end{subfigure}
\caption{
  Recomputed and corrected scenario to replace Figure 6 of~\cite{krenz2019high}.
}
\end{figure}
% Settings: visc 0.1, refine: 1.5, coarse: -0.5
\paragraph{Cosine Bubble (Sec. 4.2, Fig.~4 and~5 of~\cite{krenz2019high})}
We ran the cosine bubble scenario with and without adaptive mesh refinement (AMR) using the correct background pressure and a viscosity of $\mu=0.1$. 
The new result (\cref{fig:cosine-bubble-2d-dg-amr}) shows a very close agreement with the original results.
The adapted mesh of the new results is slightly different.
However, the mesh refinements for the two scenarios are of the same quality
Similar to the original results, the results obtained with a statically refined mesh are visually indistinguishable from the AMR results.
We also simulated a three-dimensional cosine bubble.
The results (\cref{fig:cosine-bubble-3d-dg-noamr}), computed with the correct background pressure and a viscosity of $\mu=0.4$, are similar to our original results.

\begin{figure}[htb] 
  \centering 
    \begin{minipage}[t]{.473\textwidth} 
    \centering
  \includegraphics[width=1\textwidth]{screenshots/two_bubbles_fv.png}
  \captionof{figure}{\label{fig:two-bubbles-2d-fv-noamr}%
  Recomputed and corrected scenario to replace Figure 4 in~\cite{krenz2019high}.
  2D colliding bubbles scenario, without AMR, computed with finite volume method.}
    \end{minipage}\quad% 
  \begin{minipage}[t]{.473\textwidth}
      \centering 
  \includegraphics[width=\textwidth]{screenshots/two_bubbles_dg.png}
  \captionof{figure}{\label{fig:two-bubbles-2d-dg-amr}%
  Recomputed and corrected scenario to replace Figure 5 in~\cite{krenz2019high}.
  2D colliding bubble with AMR, computed by ADER-DG method.
  Contours are at $-0.05, 0.05, \ldots 0.45$.
  }
  \end{minipage}
  \end{figure}

@@

\subsection*{Acknowledgments}
This work was funded by the European Union’s Horizon 2020 Research and Innovation Programme under grant agreements 
No~671698 (project ExaHyPE, \url{www.exahype.eu}) and 
No~823844 (ChEESE centre of excellence, \url{www.cheese-coe.eu}).
Computing resources were provided by the Leibniz Supercomputing Centre (project pr83no).

>>>>

\documentclass[runningheads]{llncs}
\title{Erratum: A High-Order Discontinuous Galerkin Solver with Dynamic Adaptive Mesh Refinement to Simulate Cloud Formation Processes }
\titlerunning{A High-Order DG Solver to Simulate Cloud Formation Processes}
\author{Lukas Krenz\orcidID{0000-0001-6378-0778} \and Leonhard Rannabauer \and Michael Bader}
\authorrunning{L.\ Krenz, L.\ Rannabauer, M.\ Bader}
\institute{TUM School of Computation, Information and Technology, Technical University of Munich\\
  \email{lukas.krenz@in.tum.de}, \email{rannabau@in.tum.de}, \email{bader@in.tum.de}
} 
\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage[american]{babel}
\usepackage[autostyle, english = american]{csquotes}
% \usepackage[%
%   backend=biber,
%   url=false,
%   doi=false,
%   % style=alphabetic,
%   % backref=true,
%   % hyperref=true,
%   maxnames=3,
%   % minnames=3,
%   % maxbibnames=99,
%   firstinits=true,
%   % uniquename=init
%   ]{biblatex}
% \addbibresource{../bibliography.bib}
\usepackage{cite}
\usepackage{todonotes}

@@

\begin{figure}[htb]
  \begin{subfigure}[t]{0.45\columnwidth}
  \includegraphics[width=\textwidth]{screenshots/cosine_bubble_2d_dg.png}
  \caption{\label{fig:cosine-bubble-2d-dg-amr}%
  2D Cosine bubble with AMR, computed by the ADER-DG method.
  Contours are at $-0.05, 0.05, \ldots 0.45$.
  }
  \end{subfigure}\quad
  \begin{subfigure}[t]{0.45\columnwidth}
  \includegraphics[width=1\textwidth]{screenshots/cosine_bubble_3d_dg.png}
  \caption{\label{fig:cosine-bubble-3d-dg-noamr}%
  3D Cosine bubble without AMR, computed by the ADER-DG method.}
  \end{subfigure}
\caption{
  Recomputed and corrected scenario to replace Figure 6 of~\cite{krenz2019high}.
}
\end{figure}
% Settings: visc 0.1, refine: 1.5, coarse: -0.5
\paragraph{Cosine Bubble (Sec. 4.2, Fig.~4 and~5 of~\cite{krenz2019high})}
We ran the cosine bubble scenario with and without adaptive mesh refinement (AMR) using the correct background pressure and a viscosity of $\mu=0.1$. 
The new result (\cref{fig:cosine-bubble-2d-dg-amr}) shows a very close agreement with the original results.
The mesh refinements for the two scenarios are not identical but of the same quality
Similar to the original results, the results obtained with a statically refined mesh are visually indistinguishable from the AMR results.
We also simulated a three-dimensional cosine bubble.
The results (\cref{fig:cosine-bubble-3d-dg-noamr}), computed with the correct background pressure and a viscosity of $\mu=0.4$, are similar to our original results.

\begin{figure}[htb] 
  \centering 
    \begin{minipage}[t]{.473\textwidth} 
    \centering
  \includegraphics[width=1\textwidth]{screenshots/two_bubbles_fv.png}
  \captionof{figure}{\label{fig:two-bubbles-2d-fv-noamr}%
  2D colliding bubbles scenario, without AMR, computed with Finite Volume method.
  Recomputed and corrected scenario to replace Figure 4 in~\cite{krenz2019high}.%
  }
    \end{minipage}\quad% 
  \begin{minipage}[t]{.473\textwidth}
      \centering 
  \includegraphics[width=\textwidth]{screenshots/two_bubbles_dg.png}
  \captionof{figure}{\label{fig:two-bubbles-2d-dg-amr}%
  2D colliding bubble with AMR, computed by ADER-DG method.
  Contours are at $-0.05, 0.05, \ldots 0.45$.
  Recomputed and corrected scenario to replace Figure 5 in~\cite{krenz2019high}.%
  }
  \end{minipage}
  \end{figure}

@@

%\subsection*{Acknowledgments}
%This work was funded by the European Union’s Horizon 2020 Research and Innovation Programme under grant agreements 
%No~671698 (project ExaHyPE, \url{www.exahype.eu}) and 
%No~823844 (ChEESE centre of excellence, \url{www.cheese-coe.eu}).
%Computing resources were provided by the Leibniz Supercomputing Centre (project pr83no).
